Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-04-12 manuscript/manuscript_pve.Rmd
BM edits

#Summary
- Interpreting limitations to plant growth requires accounting of carbon (C) mass balance between uptake and allocation. This study manipulated soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.

@@

#Introduction

Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration. As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissues sinks. At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and plant growth. At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], disrupting the coordination between *A*~n~ and growth. This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity.

As plant growth cannot simply be determined by *A*~n~, growth models must take into account several simultanesous processes affecting the C balance at any given time [@fourcaud2008plant].

Despite a wealth of studies, large uncertainties still remain regarding the coordination of C supply and growth of woody species.
*when growth is limited* interpretations of how the C balance reponds.......

@@

##Conclusions
With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings. This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants has seldom been studied. Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition. The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role]. Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity. K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for C. Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate. Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents. The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.

>>>>

#Summary

- The difficulty in quantifying all components of plant carbon (C) balance inhibits our ability to interpret growth limitation in woody species. This study manipulated soil volume to test how growth is coupled to physiology, C allocation, and sink activity in *Eucalyptus tereticornis* seedlings.

@@

#Introduction
Understanding plant growth and its relationship to C assimilation requires knowledge of the mass balance that must be achieved between C uptake and subsequent allocation to growth, storage, and respiration. As woody plants have highly integrated systems of competing carbohydrate sinks [@kozlowski1992carbohydrate], growth is driven by the allocation of photosynthate from source leaves among these different tissue sinks. At long enough time scales leaf photosynthesis (*A*~n~) and respiratory losses together determine net C balance and plant growth. At shorter temporal scales growth can instead be mediated by tissue C storage pools [@chapin1990ecology], which disrupts the coordination between *A*~n~ and growth. This discrepancy has led to the current debate on how strongly plant growth is controlled by either source or sink activity. As plant growth cannot be simply determined by *A*~n~, growth models must take into account several simultaneous processes affecting the C balance at any given time [@fourcaud2008plant]. Whether growth limitation in woody species is driven mostly by *A*~n~ or other components of the C balance remains largely uncertain.

@@

##Conclusions
With a novel field-based design we detected a massive effect of container volume on seedling growth, when compared with naturally planted seedlings. This is important as manipulations of plants grown in containers are often used to draw conclusions about growth and physiological principles, but how these results actually reflect field-grown plants is seldom studied. Although biomass partitioning was conserved, our empirical and model results suggest that the amount of photosynthate allocated to non-biomass pools such as TNC or respiration were likely altered by sink inhibition. The debate over how rates of photosynthesis affect plant growth or to what degree these rates are instead controlled by growth has existed for decades [@sweet1966role]. Our combined empirical and modeling approach shows that when non-photosynthetic parameters were kept constant, changes in *A*~n~ were not able to fully to predict changes in growth, an important distinction often missed in studies that manipulate source/sink activity. K&#246;rner [-@korner2013growth] suggests that it is the norm for sink activity to feedback onto source activity, causing growth to control *A*~n~ through the demand for C. Although this may be true, our results imply that quantifying the fate of assimilated C into known pools of growth, storage and C loss are needed prior to addressing this debate. Our modelling results agree with conclusions from Valentine and M&#228;kel&#228; [-@valentine2005bridging] where the problem with predicting tree growth is a problem in forecasting the assimilation and allocation of C and other constituents. The approach used here has the flexibility to account for multiple drivers of C allocation and provides an avenue to address future questions regarding the impact of environmental change on plant growth.
